R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-07-04 paper.tex
ICPR 1st revised version

@@

{%
  \newenvironment{mycomment}{
    \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
      }{\end{minipage}}
  \section*{Reviewer Response}
  We would like to appriciate all the reviewers for their very helpful comments.
  We added an overview of other existing methods, discussion about parameter
  selection, and comparisons between Anchor and R-LIME\@.
  Below are suggestions from reviewers and our response.

  \subsection*{Reviewer \#1}
  Suggestions for Rebuttal:
  \begin{enumerate}
    \setlength{\itemsep}{15pt}
    \item Offer guidance on how to select optimal parameters for different
          datasets and models.

          \begin{mycomment}
            Thank you for your suggestion. We added guidance on how parameters
            should be selected in practical use cases to \cref{sec:discussion}.
          \end{mycomment}

          \begin{mycomment}
            Thank you for your suggestion. We added an overview of other
            model-agnostic interpretability methods to \cref{sec:related-work}.
          \end{mycomment}

          \begin{mycomment}
            Thank you for your suggestion. We additionally conducted qualitative
            and quantitative comparisons between Anchor and R-LIME,
            which demonstrated that R-LIME is more effective than Anchor.
          \end{mycomment}
  \end{enumerate}

  \subsection*{Reviewer \#4}
  The authors should kindly explain why there is not a quantitative comparison
  between their proposed method R-LIME and Anchor. The lack of the comparison
  makes it hard to evaluate the impact of the proposed model.

  \begin{mycomment}
    Thank you for your insightful comments.
  \end{mycomment}

  \subsection*{Reviewer \#5}
  \begin{itemize}
    \setlength{\itemsep}{15pt}
    \item It would be beneficial to move the comparison of R-LIME with Anchor
          and LIME to the Related Work section for improved clarity and
          organization.

          \begin{mycomment}
            Thank you for your suggestion.

            \ldots
          \end{mycomment}

          \begin{mycomment}
            Thank you for your valuable feedback.
            It is true that there are theoretical issues for using the KL-LUCB
            algorithm, although our results suggest that its practical effect
            is negligible.
            We leave the issues to the future work because of our limited time.
          \end{mycomment}

          \begin{mycomment}
            Thank you for your suggestion. We renamed the section to `Discussion'.
          \end{mycomment}
  \end{itemize}
}

% Reset page number and typeset title
\newpage
\setcounter{page}{1}
\maketitle

@@

\section{Introduction}
In recent years,
complex machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvement in accuracy.
However,
their increasing complexity and black-box nature pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the opacity of decision process becomes a major obstacle to implementation.
In order to address this problem,
there has been extensive research in the field of post-hoc explanations
for machine learning models~\cite{%
  guidotti2018local,radulovic2023bella,ribeiro2016why,ribeiro2018anchors}.
Existing post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
and the latter are further classified into \emph{global} and \emph{local} methods
based on their locality in input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \vspace{-2.24cm}
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

@@

They are broadly divided into
\emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure.
Model-dependent methods,
such as deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
and layer-wise relevance propagation (LRP)~\cite{bach2015pixel},
most of which focus on neural networks and
explain the model's behavior using its parameters~\cite{samek2021explaining}.
While these methods provide detailed explanations
(e.g., layer-wise explanations for neural networks),
it is often challenging
to apply the same method to models with different structures.
On the other hand,
model-agnostic methods use only the output of the model.
Although they are applicable to any model,
they cannot explain the reasoning process inside the model.

Furthermore, model-agnostic methods are categorized into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as partial dependence plots (PDP)~\cite{friedman2001greedy}
and accumulated local effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as local interpretable model-agnostic explanations
(LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
\hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
explain model's behavior in the vicinity of a specific input.
While they offer explanations more simple and accurate
than global methods,
the scope of the explanation is limited locally.

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp-setting}
{%
  \renewcommand{\arraystretch}{1.05}
  \begin{table}[tbp]
    \centering
    \caption[Attributes of the recidivism dataset used in the experiments]{%
      Attributes of the recidivism dataset used in the experiments.
      Continuous features are all discretized,
      and only binary and ordinal features are considered.
    }\label{tab:rcdv}
    \begin{tabular}{llc}
      \toprule
      Attribute              & Overview                              & \# of Possible Values \\
      \midrule
      Race                   & Race (Black or White)                 & 2                     \\
      Alcohol                & Presence of serious alcohol issues    & 2                     \\
      Junky                  & Drug usage                            & 2                     \\
      Supervised Release     & Supervised release                    & 2                     \\
      Married                & Marital status                        & 2                     \\
      Felony                 & Felony or not                         & 2                     \\
      WorkRelease            & Participation in work release program & 2                     \\
      Crime against Property & Crime against property or not         & 2                     \\
      Crime against Person   & Crime against a person or not         & 2                     \\
      Gender                 & Gender (Female or Male)               & 2                     \\
      Priors                 & Number of prior offenses              & 4                     \\
      YearsSchool            & Years of formal education completed   & 4                     \\
      PrisonViolations       & Number of prison rule violations      & 3                     \\
      Age                    & Age                                   & 4                     \\
      MonthsServed           & Months served in prison               & 4                     \\
      \midrule
      Recidivism             & Recidivism or not                     & 2                     \\
      \bottomrule
    \end{tabular}
  \end{table}
}

@@

    \def\dir{src/experiments/exp1/ver1/examples/output}
    \def\Asample{0012}
    \def\Bsample{0011}
    \def\index#1{\ifnum#1=0 \Asample\else\Bsample\fi}

    {%
      \def\AB#1{\ifnum#1=0 A\else B\fi}
      \renewcommand{\arraystretch}{1.02}
      \begin{figure}[tbp]
        \foreach\a in {0,1}{%
            \centering
            \begin{subfigure}{\textwidth}
              \centering
              \begin{tabular}{p{14em}m{16em}}
                \toprule
                \csvreader[no head, late after line= \\]{%
                  \dir/\index{\a}.csv
                }{}{%
                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii % chktex 1
                }
                \bottomrule
              \end{tabular}
              \caption{Instance~\AB{\a}}
              \vspace{15pt}
            \end{subfigure}
          }
        \vspace{-15pt}
        \caption[Two instances sampled from recidivism dataset]{%
          Two instances sampled from training data of recidivism dataset.
          Each number in parentheses represents the integer value assigned
          to the corresponding categorical value.
        }\label{fig:instance}
      \end{figure}
    }
    {%
      \def\scale{0.315}
      \def\dir{exp1/ver1/examples/output}
      \def\imgwidth{0.3\textwidth}
      \def\hspacebase{\hspace{-1.5em}}
      \def\vspacebase{\vspace{0.5em}}
      \def\vspacebeforecaption{\vspace{-0.4em}}

      \newcommand{\limesubfigure}[2]{
        \begin{subfigure}[t]{\textwidth}
          \hspace{#2}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-\index{#1}}
          \caption{LIME}\label{fig:lime-#1}
          \vspace{1.0em}
        \end{subfigure}
      }
      \newcommand{\anchorsubfigure}[1]{
        \foreach{\a} in {70,80,90}{
            \begin{subfigure}[t]{\textwidth}
              \centering
              \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-\index{#1}-\a}
              \caption{\hl{Anchor ($\tau=0.\a$)}}
              \vspace{1.0em}
            \end{subfigure}
          }
      }
      \newcommand{\rlimesubfigure}[3]{
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{#3}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-\index{#1}-#2}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.#2$)}\label{fig:rlime-#1-#2}
          \vspacebase{}
        \end{subfigure}
      }
      \begin{figure}[t]
        \begin{subfigure}[t]{0.45\textwidth}
          \centering
          \limesubfigure{0}{-10pt}
          \anchorsubfigure{0}
        \end{subfigure}
        \hfill
        \begin{subfigure}[t]{0.45\textwidth}
          \rlimesubfigure{0}{70}{-10pt}

          \vspace{12pt}
          \rlimesubfigure{0}{90}{-22pt}
        \end{subfigure}
        \caption[Explanation for Instance A by LIME and R-LIME]{%
          Explanation for Instance A by LIME and R-LIME\@.
        }\label{fig:A}
      \end{figure}
      \begin{figure}[t]
        \begin{subfigure}[t]{0.45\textwidth}
          \limesubfigure{1}{-30pt}
          \anchorsubfigure{1}
        \end{subfigure}
        \hfill
        \begin{subfigure}[t]{0.45\textwidth}
          \rlimesubfigure{1}{70}{-10pt}

          \vspace{18pt}
          \rlimesubfigure{1}{90}{-25pt}
        \end{subfigure}
        \caption[Explanation for Instance B by LIME and R-LIME]{%
          Explanation for Instance B by LIME and R-LIME\@.
        }\label{fig:B}
      \end{figure}
    }
  }
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each feature name represent the contribution
(weight of the linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures display the 5 features with the highest absolute contribution.

@@

@@

\subsection{Quantitative Evaluation: LIME vs. R-LIME}

@@

\subsubsection{Experimental Results}
The results are presented in \cref{fig:box-plot},
showing the distribution of the local accuracy of the linear classifiers
learned by LIME and R-LIME\@.
R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
This suggests that the linear classifiers learned by LIME and R-LIME
differ significantly,
and R-LIME learns a high-accuracy linear classifier
adapted to the optimized rectangular region.
Additionally, as $\tau$ increases,
the variability in the accuracy of LIME widens.
This indicates that the linear classifiers learned by LIME may not function
effectively as approximation models depending on how the region is selected.

\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}
\subsubsection{\hl{Experimental Setup}}
\hl{
  To demonstrate that R-LIME explanations are more general than Anchor,
  we conducted a comparison of the coverage of explanations
  between Anchor and R-LIME\@.
  Under the same settings as in
}\cref{sec:exp-setting},
\hl{
  we generated Anchor and R-LIME explanations
  for 100 instances from the test data of the recidivism dataset,
  under the values of $\tau=0.70,0.80,0.90$.
}

@@

\section{\hl{Discussion}}\label{sec:discussion}
{%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
}

@@

@@

\bibliographystyle{src/style/splncs04}
\bibliography{src/myref/myref}

>>>>

\newenvironment{mycomment}{
  \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
    }{\end{minipage}}

\section*{Reviewer Response}
We deeply appriciate all the reviewers who made valuable and insightful comments
on our paper and gave us the opportunity to submit a revised version.
We have done our best for the revision according to their comments as shown below.
We also would like to thank in advance all the reviewers for reconsidering
the suitability of our revised paper for the conference.

\subsection*{Summary of revisions}
We would like to appriciate all the reviewers for their clear and insightful
comments.
We improved our paper from the original version according to their comments.
The major revision points are listed as follows:
\begin{enumerate}
  \item We added an overview of other existing methods to \cref{sec:related-work}.
  \item We added discussion about parameter selection in \cref{sec:param}.
  \item We conducted comparisons between Anchor and R-LIME to \cref{sec:related-work}.
\end{enumerate}
Please see below for a point-by-point response to each reviewer's comments.

\subsection*{Responding to Reviewer \#1}
Suggestions for Rebuttal:
\begin{enumerate}
  \setlength{\itemsep}{15pt}
  \item Offer guidance on how to select optimal parameters for different
        datasets and models.

        \begin{mycomment}
          We would appreciate for your suggestion.
          We added \cref{sec:param} as a guidance on how parameters should be
          selected in practice.
        \end{mycomment}

        \begin{mycomment}
          Thank you for your valuable suggestion.
          We should add an overview of other model-agnostic interpretability
          methods, but we only added names of some other methods to
          \cref{sec:related-work} because of lack of space.
        \end{mycomment}

        \begin{mycomment}
          We would like to appriciate your sharp observations.
          We additionally conducted qualitative and quantitative comparisons
          between Anchor and R-LIME,
          which demonstrated that R-LIME generates more informative and
          general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
        \end{mycomment}
\end{enumerate}
\subsection*{Responding to Reviewer \#4}
The authors should kindly explain why there is not a quantitative comparison
between their proposed method R-LIME and Anchor. The lack of the comparison
makes it hard to evaluate the impact of the proposed model.

\begin{mycomment}
  We would appreciate for your insightful comments.
  We additionally conducted qualitative and quantitative comparisons
  between Anchor and R-LIME,
  which demonstrated that R-LIME generates more informative and
  general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
\end{mycomment}

\subsection*{Responding to Reviewer \#5}
\begin{itemize}
  \setlength{\itemsep}{15pt}
  \item It would be beneficial to move the comparison of R-LIME with Anchor
        and LIME to the Related Work section for improved clarity and
        organization.

        \begin{mycomment}
          We would like to appriciate for your insightful suggestion.
          We interpreted your suggestrion to mean that we should move
          \cref{fig:example} and its explanation to \cref{sec:related-work}.
          We discussed about the most understandable structure of our paper.
          And for clarity, we concluded that we should present effectiveness
          of R-LIME compared to existing methods closely related to our method
          in \cref{sec:introduction},
          before we overview other existing methods in \cref{sec:related-work}.
        \end{mycomment}

        \begin{mycomment}
          Thank you for your valuable feedback.
          It is true that we must address theoretical issues for using
          KL-LUCB algorithm, although our results suggest that its practical
          effect is negligible.
          We focus on presenting our novel framework for local interpretability,
          not on the detailed algorithm.
          Thus, we leave the issues for future work because of lack of space.
          But we deeply appreciate for your sharp observations.
        \end{mycomment}

        \begin{mycomment}
          Thank you for your suggestion. We renamed the section to `Discussion'
          for clearly reflecting the content.
        \end{mycomment}
\end{itemize}

\newcommand{\sampleindex}[1]{\ifnum#1=0 \Asample\else\Bsample\fi}
\def\AB#1{\ifnum#1=0 A\else B\fi}

\def\paper{

@@

\maketitle

@@

\section{Introduction}\label{sec:introduction}
In recent years,
complex machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvement in accuracy.
However,
their increasing complexity and black-box nature pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the opacity of decision process becomes a major obstacle to implementation.
In order to address this problem,
there has been extensive research in the field of post-hoc explanations
for machine learning models
~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
Existing post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
and the latter are further classified into \emph{global} and \emph{local} methods
based on their locality in input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \vspace{-2.24cm}
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

@@

They are broadly divided into
\emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure.
Model-dependent methods,
such as deep Taylor decomposition (DTD)~\cite{montavon2017explaining}
and layer-wise relevance propagation (LRP)~\cite{bach2015pixel},
most of which focus on neural networks and
explain the model's behavior using its parameters~\cite{samek2021explaining}.
While these methods provide detailed explanations
(e.g., layer-wise explanations for neural networks),
it is often challenging
to apply the same method to models with different structures.
In contrast,
model-agnostic methods use only the model's output.
Although they are applicable to any model,
they cannot explain the reasoning process inside the model.

Furthermore, model-agnostic methods are categorized into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as partial dependence plots (PDP)~\cite{friedman2001greedy}
and accumulated local effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as \hl{indivisual conditional expectation (ICE)}~\cite{goldstein2015peeking},
local interpretable model-agnostic explanations
(LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
\hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
explain model's behavior in the vicinity of a specific input.
While they offer explanations more simple and accurate
than global methods,
the scope of the explanation is limited locally.

@@

\subsection{Qualitative Evaluation}\label{sec:exp-qual}
\subsubsection{Experimental Setup}\label{sec:exp-setting}
{%
  \renewcommand{\arraystretch}{1.05}
  \begin{table}[tbp]
    \centering
    \caption[Attributes of the recidivism dataset used in the experiments]{%
      Attributes of the recidivism dataset used in the experiments.
      Continuous features are all discretized,
      and only binary and ordinal features are considered.
    }\label{tab:rcdv}
    \begin{tabular}{llc}
      \toprule
      Attribute              & Overview                              & \# of Possible Values \\
      \midrule
      Race                   & Race (Black or White)                 & 2                     \\
      Alcohol                & Presence of serious alcohol issues    & 2                     \\
      Junky                  & Drug usage                            & 2                     \\
      Supervised Release     & Supervised release                    & 2                     \\
      Married                & Marital status                        & 2                     \\
      Felony                 & Felony or not                         & 2                     \\
      WorkRelease            & Participation in work release program & 2                     \\
      Crime against Property & Crime against property or not         & 2                     \\
      Crime against Person   & Crime against a person or not         & 2                     \\
      Gender                 & Gender (Female or Male)               & 2                     \\
      Priors                 & Number of prior offenses              & 4                     \\
      YearsSchool            & Years of formal education completed   & 4                     \\
      PrisonViolations       & Number of prison rule violations      & 3                     \\
      Age                    & Age                                   & 4                     \\
      MonthsServed           & Months served in prison               & 4                     \\
      \midrule
      Recidivism             & Recidivism or not                     & 2                     \\
      \bottomrule
    \end{tabular}
  \end{table}
}

@@

    \def\dir{src/experiments/exp1/ver1/examples/output}
    \def\Asample{0012}
    \def\Bsample{0011}

    {%
      \renewcommand{\arraystretch}{1.02}
      \begin{figure}[tbp]
        \foreach\a in {0,1}{%
            \centering
            \begin{subfigure}{\textwidth}
              \centering
              \begin{tabular}{p{14em}m{16em}}
                \toprule
                \csvreader[no head, late after line= \\]{%
                  \dir/\sampleindex{\a}.csv
                }{}{%
                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii % chktex 1
                }
                \bottomrule
              \end{tabular}
              \caption{Instance~\AB{\a}}
              \vspace{15pt}
            \end{subfigure}
          }
        \vspace{-15pt}
        \caption[Two instances sampled from recidivism dataset]{%
          Two instances sampled from training data of recidivism dataset.
          Each number in parentheses represents the integer value assigned
          to the corresponding categorical value.
        }\label{fig:instance}
      \end{figure}
    }
  }

\input{src/fig-examples}
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each feature name represent the contribution
(weight of the linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures display the 5 features with the highest absolute contribution.

@@

\hl{
  Anchor provides conditions for the model's output to be fixed with high
  probability.
  For example,
  the explanation for instance A under $\tau=0.70$
} (\cref{fig:anchor-0-70})
\hl{
  means that the model will predict with 75.66 \% probability
  that the prisoner will commit no more crimes
  when a prisoner is older than 33 and has one prior offense.
  Although it clearly provides the explanation's application scope,
  it does not provide details about how these conditions affect the model's output.
}

@@

\vspace{-1pt}
\subsection{Quantitative Evaluation: LIME vs. R-LIME}

@@

\vspace{-5pt}
\subsubsection{Experimental Results}
The results are presented in \cref{fig:box-plot},
showing the distribution of the local accuracy of the linear classifiers
learned by LIME and R-LIME\@.
R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
This suggests that the linear classifiers learned by LIME and R-LIME
differ significantly,
and R-LIME learns a high-accuracy linear classifier
adapted to the optimized rectangular region.
Additionally, as $\tau$ increases,
the variability in the accuracy of LIME widens.
This indicates that the linear classifiers learned by LIME may not function
effectively as approximation models depending on how the region is selected.

\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}\label{sec:exp-anchor}
\subsubsection{\hl{Experimental Setup}}
\hl{
  To demonstrate that R-LIME explanations are more general than Anchor,
  we conducted a comparison of the coverage of explanations
  between Anchor and R-LIME\@.
  Under the same settings as in
}\cref{sec:exp-setting},
\hl{
  we generated Anchor and R-LIME explanations
  for 100 instances from the test data of the recidivism dataset,
  under the values of $\tau=0.70,0.80,0.90$.
}

@@

\section{\hl{Discussion}}
 {%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
 }

@@

\subsection{\hl{Parameter Selection}}\label{sec:param}

\hl{
  R-LIME requires some hyperparameters to be selected by users,
  such as the threshold of accuracy $\tau$, beam width $B$, tolerance $\epsilon$
  and confidence level $\delta$.
  $B$ should be large and $\epsilon$ and $\delta$ should be small for
  accurate results, as long as the computational cost is acceptable.
  $\tau$ should be carefully selected by users, sometimes interactively,
  considering the tradeoff between
  the accuracy and generality of the explanation.
}

@@

\newpage
\bibliographystyle{src/style/splncs04}
\bibliography{src/myref/myref}
}

% Reset page number and typeset title
\newpage
\setcounter{page}{1}
\paper{}
\renewcommand{\hl}[1]{#1}
% \newpage
% \setcounter{page}{1}
% \paper{}
